Towards Bringing Together Numerical Methods for Partial Differential Equation and Image Processing

### 2020-03-25 paper/eccv2020submission.tex
Adding the conclusion

\documentclass{llncs}
\usepackage[title]{appendix}
\usepackage[pagebackref]{hyperref}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{comment}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{color}

\newcommand{\reffig}[1]{\hyperref[#1]{Figure \ref*{#1}}}
\newcommand{\refsec}[1]{\hyperref[#1]{Section \ref*{#1}}}
\newcommand{\reftab}[1]{\hyperref[#1]{Table \ref*{#1}}}
\newcommand{\refapp}[1]{\hyperref[#1]{Appendix \ref*{#1}}}
\DeclareMathOperator*{\argminA}{arg\,min} % Jan Hlavacek

@@

\begin{document}
% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
% \linenumbers
\pagestyle{headings}
\mainmatter
\def\ECCVSubNumber{100}  % Insert your submission number here

\title{Towards Bringing Together Numerical Methods for Partial Differential Equation and Deep Neural Networks} % Replace with your title

@@

We did not construct a single holistic model that can handle all of the simulation's parameters. Our efforts were concentrated on building a couple of smaller ones that take into account subsets of the parameters. The studied models are:
\begin{list}{$\circ$}{}
\item a constant model --- does not take into any of the parameters and it is trained with data from a single simulation. It is conceived as a baseline and proof of concept model that is there to show how a neural network can learn to generate simulation timesteps in from of images.
\item A fluid inflow speed model --- the model receives the inflow speed of the fluid as an extra input. It is trained with data from several simulations with different inflow speeds.
\item A viscosity and density model --- the model receives the viscosity and density of the fluid as extra inputs.
\end{list}
By evaluating each models we want to see how a network can generalize each of the parameter subsets and to what extent

\subsection{Simulation Setup and Data generation}
\emph{To study the performance of conditional GANs on generating frames of the concrete simulation we generated the training data ourselves. In what follows we give details about the process.} The training data was generated by performing numerous simulations of an incompressible fluid flow around a rectangular object in a channel. The simulations were modeled according to the Navier-Stokes equations for incompressible flow. Because we are interested in the image representations of the simulations, we are dealing only with the 2D case. There are several boundary conditions that describe the simulation setup:
\begin{list}{$\circ$}{}
\item Inflow condition on the left side of the channel
\item Outflow condition on the right side of the channel
\item No slip condition on bottom and top side of the channel as well as the sides of the object.
\end{list}
The simulation setup has three separate adjustable parameters --- inflow speed $g$, fluid density $\rho$ and fluid viscosity $\nu$.
\\
We generated three sets of simulations for training the three kinds of models.
\begin{list}{$\circ$}{}
\item constant: a single simulation with \ldots.
\item varying inflow speed: \ldots simulations with different inflow speed. The inflow speeds are in the range of \ldots with a step of \ldots.
\item varying viscosity and density of the fluid: \ldots simulations all with different fluid viscosity and density. The viscosity was in the range of \ldots with a step of \ldots and the density was in the range of \ldots with a step of \ldots. We used the product of the two parameter ranges to perform simulations with all of the possible combinations between the two parameters.
\end{list}

@@

\noindent\textbf{Details Evaluation:}
\emph{In this subsection we want to give several details on the training and evaluating approach}
\begin{itemize}
\item All models were trained from scratch and no pretraining or transfer-learning was undertaken.
\item For each model, the whole training and evaluating procedure was done ten times with different seeds for the random number generators of our python scripts. We report the results of each run and give them in a form of error plots or explicitly give the variance of all runs.
\item All of the reported results of for the individual runs are averaged across the simulation frames in the training sets.
\item While performing the experiments, we did not tweak the hyper parameters of the models excessively. We did, however, tried several sets of hyper parameters until the models achieved satisfactory results. The exact hyper parameters are given in []
\end{itemize}

@@

@@

The concrete encoder-decoders for each model type are as follows:
\begin{itemize}
\item[\cdot] Constant model:\newline
  \emph{Encoder}: \texttt{C32-C64-C128-C256-C256-C256}\newline
  \emph{Decoder}: \texttt{CD256-C512-C512-C256-C128-C64}
\item[\cdot] Inflow speed model:\newline
  \emph{Encoder}: \texttt{C48-C96-C192-C384-C384-C384}\newline
  \emph{Decoder}: \texttt{CD384-C768-C768-C384-C192-C96}
\item[\cdot] Viscosity-Density model:\newline
  \emph{Encoder}: \texttt{C64-C128-C256-C512-C512-C512} \newline
  \emph{Decoder}: \texttt{CD512-C1024-C1024-C512-C256-C128}
\end{itemize}

@@

% LocalWords:  Convolutional timestep timesteps grayscale cGANs

>>>>

\documentclass{llncs}
\usepackage[title]{appendix}
\usepackage[pagebackref]{hyperref}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{comment}
\usepackage{amsmath,amssymb}
\usepackage{color}

\newcommand{\reffig}[1]{\hyperref[#1]{Figure \ref*{#1}}}
\newcommand{\refsec}[1]{\hyperref[#1]{Section \ref*{#1}}}
\newcommand{\reftab}[1]{\hyperref[#1]{Table \ref*{#1}}}
\newcommand{\refapp}[1]{\hyperref[#1]{Appendix \ref*{#1}}}
\DeclareMathOperator*{\argminA}{arg\,min}

@@

\begin{document}
% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
% \linenumbers
\pagestyle{headings}
\mainmatter
\def\ECCVSubNumber{100}

\title{Towards Bringing Together Numerical Methods for Partial Differential Equation and Image Processing}

@@

We did not construct a single holistic model that can handle all of the simulation's parameters. Our efforts were concentrated on building a couple of smaller ones that take into account subsets of the parameters. The studied models are:
\begin{list}{$\circ$}{}
\item[$\cdot$] a constant model --- does not take into any of the parameters and it is trained with data from a single simulation. It is conceived as a baseline and proof of concept model that is there to show how a neural network can learn to generate simulation timesteps in from of images.
\item[$\cdot$] A fluid inflow speed model --- the model receives the inflow speed of the fluid as an extra input. It is trained with data from several simulations with different inflow speeds.
\item[$\cdot$] A viscosity and density model --- the model receives the viscosity and density of the fluid as extra inputs.
\end{list}
By evaluating each models we want to see how a network can generalize each of the parameter subsets and to what extent

\subsection{Simulation Setup and Data generation}
\emph{To study the performance of conditional GANs on generating frames of the concrete simulation we generated the training data ourselves. In what follows we give details about the process.} The training data was generated by performing numerous simulations of an incompressible fluid flow around a rectangular object in a channel. The simulations were modeled according to the Navier-Stokes equations for incompressible flow. Because we are interested in the image representations of the simulations, we are dealing only with the 2D case. There are several boundary conditions that describe the simulation setup:
\begin{list}{$\circ$}{}
\item[$\cdot$] Inflow condition on the left side of the channel
\item[$\cdot$] Outflow condition on the right side of the channel
\item[$\cdot$] No slip condition on bottom and top side of the channel as well as the sides of the object.
\end{list}
The simulation setup has three separate adjustable parameters --- inflow speed $g$, fluid density $\rho$ and fluid viscosity $\nu$.
\\
We generated three sets of simulations for training the three kinds of models.
\begin{list}{$\circ$}{}
\item[$\cdot$] constant: a single simulation with \ldots.
\item[$\cdot$] varying inflow speed: \ldots simulations with different inflow speed. The inflow speeds are in the range of \ldots with a step of \ldots.
\item[$\cdot$] varying viscosity and density of the fluid: \ldots simulations all with different fluid viscosity and density. The viscosity was in the range of \ldots with a step of \ldots and the density was in the range of \ldots with a step of \ldots. We used the product of the two parameter ranges to perform simulations with all of the possible combinations between the two parameters.
\end{list}

@@

\noindent\textbf{Details Evaluation:}
\emph{In this subsection we want to give several details on the training and evaluating approach}
\begin{itemize}
\item[$\cdot$] All models were trained from scratch and no pretraining or transfer-learning was undertaken.
\item[$\cdot$] For each model, the whole training and evaluating procedure was done ten times with different seeds for the random number generators of our python scripts. We report the results of each run and give them in a form of error plots or explicitly give the variance of all runs.
\item[$\cdot$] All of the reported results of for the individual runs are averaged across the simulation frames in the training sets.
\item[$\cdot$] While performing the experiments, we did not tweak the hyper parameters of the models excessively. We did, however, tried several sets of hyper parameters until the models achieved satisfactory results. The exact hyper parameters are given in []
\end{itemize}

@@

The results presented in this paper suggest that solving a numerical task trough image-to-image translation is can be a viable approach. We showed how conditional GANs can be used to learn the image representations of the solutions of a fluid simulation according to the Navier-Stokes equations. We built several models that can generalize different parts of the parameters of the simulations and gave concrete numbers that quantify the results.

We see our work as a preliminary research and we believe that the approach can be further developed and investigated. Strategies for improving the models that were considered but not implemented include:
\begin{itemize}
\item[$\cdot$] using a LSTM layer in the networks --- our models have the limitation that during training they don't know about the artifact on the images caused by themselves. We think a LSTM layer can mitigate this problem.
\item[$\cdot$] preprocessing the input for and postprocessing the output of the networks --- morphological operations like opening and closing can also be used to minimize the artifacts in the predicted frames.
\item[$\cdot$] further investigation of the effects of using RGB-images instead of grayscale ones.
\end{itemize}

@@

The concrete encoder-decoders for each model type are as follows:
\begin{itemize}
\item[$\cdot$] Constant model:\newline
  \emph{Encoder}: \texttt{C32-C64-C128-C256-C256-C256}\newline
  \emph{Decoder}: \texttt{CD256-C512-C512-C256-C128-C64}
\item[$\cdot$] Inflow speed model:\newline
  \emph{Encoder}: \texttt{C48-C96-C192-C384-C384-C384}\newline
  \emph{Decoder}: \texttt{CD384-C768-C768-C384-C192-C96}
\item[$\cdot$] Viscosity-Density model:\newline
  \emph{Encoder}: \texttt{C64-C128-C256-C512-C512-C512} \newline
  \emph{Decoder}: \texttt{CD512-C1024-C1024-C512-C256-C128}
\end{itemize}

@@

% LocalWords:  Convolutional timestep timesteps grayscale cGANs
% LocalWords:  preprocessing postprocessing
